Verification of the CVM algorithm with a New Recursive Analysis Technique

### 2025-02-23 paper/sec/conclusion.tex
conclusion edit

\section{Conclusion}\label{sec:conclusion}
We have presented the first formalization of the CVM algorithm using Isabelle/HOL.
Central to our formalization is a novel invariant-based proof technique for randomized algorithms which is inspired by our alternative approach to analyzing the CVM algorithm via the Cram\'{e}r--Chernoff method.
Interestingly, the technique readily generalized to a new CVM variant with stronger properties (totality and unbiasedness)---we formalized this version using the same invariant, together with a new library of results for negative association.
In future work, it would be interesting to formalize other variations subsampling variants of CVM.
More generally, it would be interesting to explore whether the technique could be applied towards proving other randomized (streaming) algorithms.

>>>>

\section{Conclusion}\label{sec:conclusion}
We presented the first formalization of the CVM algorithm using Isabelle/HOL.
Central to our formalization is a novel invariant-based proof technique for randomized algorithms which is inspired by our alternative analysis of the CVM algorithm via the Cram\'{e}r--Chernoff method.
Interestingly, the technique readily generalized to a new CVM variant with stronger properties (totality and unbiasedness)---we formalized this latter version using the same invariant, together with a new library of results for negative association.
In future work, it would be interesting to formalize other variations of subsampling for CVM.
More generally, one could further explore whether the technique we introduced here could be applied towards proofs of other randomized (streaming) algorithms.
